19Q2

### 2019-07-23 19Q2.Rmd

### Lineages

```{r, eval=FALSE}
ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)

ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)

gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
gdsc_filt <- unfactorize(gdsc_filt)

genes <- union(unique(ccle_signif_dgl$Gene), union(unique(ctrp_signif_dgl$Gene), unique(gdsc_signif_dgl$Gene)))
diseases <- union(unique(ccle_signif_dgl$disease), union(unique(ctrp_signif_dgl$disease), unique(gdsc_signif_dgl$disease)))

ccle_signif_dgl_4plot <- merge(merge(ccle_signif_dgl, unique(select(ccle_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
ccle_signif_dgl_4plot$Database <- "CCLE"

ctrp_signif_dgl_4plot <- merge(merge(ctrp_signif_dgl, unique(select(ctrp_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
ctrp_signif_dgl_4plot$Database <- "CTRP"

gdsc_signif_dgl_4plot <- merge(merge(gdsc_signif_dgl, unique(select(gdsc_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
gdsc_signif_dgl_4plot$Database <- "GDSC"
```

@@

```{r wilcoxon_heatmap_function}
MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius, na_color) {
  if(missing(na_color)) {
    na_color <- "white"
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]

@@

    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = na_color,
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.07, gp = gpar(fontsize = 17))

@@

```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.03)
png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.03)
png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                              ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.03, na_color = "black")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                               ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015, na_color = "black")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.015, na_color = "black")
png(filename = "./plots/manuscript/drug_prot_heatmap.png", width = 13, height = 5, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

```{r fus_heatmaps, eval=FALSE}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.1)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.1)
png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

@@

```{r}
MakeWilcoxonLineageHeatmap <- function(all_lin_df, lineage) {
  use_data <- filter(all_lin_df, Gene %in% unique(g2p_mut$Gene) & disease == lineage)
  ccle_df <- filter(use_data, Database == "CCLE")
  ctrp_df <- filter(use_data, Database == "CTRP")
  gdsc_df <- filter(use_data, Database == "GDSC")

  ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_df, feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)

  ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_df, feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 12, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)

  ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_df, feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)

  ht <- ht_ccle + ht_ctrp + ht_gdsc
  return(ht)
}

SaveWilcoxonLineageHeatmap <- function(ht, outfile) {
  png(filename = outfile, width = 13, height = 9.5, units = "in", res = 500)
  draw(ht, gap = unit(0.25, "in"), heatmap_legend_side = "top")
  dev.off()
}
```

```{r, eval=FALSE}
diseases <- union(unique(ccle_signif_dgl_4plot$disease), union(unique(ctrp_signif_dgl_4plot$disease), unique(gdsc_signif_dgl_4plot$disease)))

drugscreens_all_signif_mut <- rbind(ccle_signif_dgl_4plot, ctrp_signif_dgl_4plot, gdsc_signif_dgl_4plot)

lin_hts <- lapply(diseases, MakeWilcoxonLineageHeatmap, all_lin_df = drugscreens_all_signif_mut)
lin_ht_paths <- paste0(lins, "_mut_heatmap.png")
pwalk(list(lin_ht_paths, lin_hts), SaveWilcoxonLineageHeatmap, outfile = "./plots/manuscript/lineage_heatmaps")
```

>>>>

@@

```{r wilcoxon_heatmap_function}
MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, na_color) {
  if(missing(na_color)) {
    na_color <- "white"
  }

  if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]

@@

    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = na_color,
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  if(color == "steelblue4") {
                    radius <- height*0.18
                  }
                  if(color == "darkgreen") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
                      radius <- height*0.18
                    }
                    else { radius <- width*0.20 }
                  }
                  if(color == "turquoise4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) {
                      radius <- height*0.18
                    }
                    else { radius <- width*0.20 }
                  }

                  grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.07, gp = gpar(fontsize = 17))

@@

```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes")
png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes")
png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                              ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                               ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
png(filename = "./plots/manuscript/drug_prot_heatmap.png", width = 13, height = 5, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

```{r fus_heatmaps, eval=FALSE}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

@@

```{r lineage_mut_heatmap_functions}
MakeWilcoxonLineageHeatmap <- function(df, database, lineage) {
  plot_colors <- c("CCLE" = "darkgreen", "CTRP" = "steelblue4", "GDSC" = "turquoise4")
  plot_breaks <- list("CCLE" = seq(0, 5, by = 1), "CTRP" = seq(0, 12, by = 2), "GDSC" = seq(0, 8, by = 2))

  df <- filter(df, disease == lineage)

  ht <- MakeWilcoxonHeatmap(signif_df = df, feature = "mutation", legend_title = paste0(database, "\n", lineage, "\n-log10(p-value)"), legend_breaks = plot_breaks[[database]], row_names = TRUE, color = plot_colors[[database]], col_title = "Drugs", row_title_txt = "Genes")

  return(ht)
}

SaveWilcoxonLineageHeatmap <- function(database, ht_list, lineage) {
  ht <- ht_list[[lineage]]
  out_height <- floor((nrow(ht@matrix) + 1) / 2) + 2
  out_width <- ncol(ht@matrix) / 2 + 1

  png(filename = paste0("./plots/manuscript/lineage_heatmaps/", tolower(database), "_", lineage, "_mut_heatmap.png"), width = out_width, height = out_height, units = "in", res = 500)
  draw(ht, heatmap_legend_side = "top")
  invisible(dev.off())
}
```

```{r lineage_mut_heatmaps, eval=FALSE, message=FALSE}
ccle_hts <- lapply(unique(ccle_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ccle_signif_dgl, database = "CCLE")
names(ccle_hts) <- unique(ccle_signif_dgl$disease)
lapply(unique(ccle_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ccle_hts, database = "CCLE")

ctrp_hts <- lapply(unique(ctrp_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ctrp_signif_dgl, database = "CTRP")
names(ctrp_hts) <- unique(ctrp_signif_dgl$disease)
lapply(unique(ctrp_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ctrp_hts, database = "CTRP")

gdsc_hts <- lapply(unique(gdsc_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = gdsc_signif_dgl, database = "GDSC")
names(gdsc_hts) <- unique(gdsc_signif_dgl$disease)
lapply(unique(gdsc_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = gdsc_hts, database = "GDSC")
```
